Predicting Tags for StackOverflow Posts

### 2013-03-18 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: e33b40fa14b137c80e377a87d94517151961170c [formerly dce291dbc8470f0a803c910627c97f35080b7b3c]
Former-commit-id: d572a56a0a2fb0dbf130932cc2f8a5084f9ebc25

The final best-fit coefficients for each model component and formal statistical measurements are included in Tables \ref{tab:coeffs} and \ref{tab:fits} respectively.
Note that all four coefficients for the run are strong predictors of tag use ($p<.01$), and model fit is satisfactory (McFadden's pseudo $R_{}^{2}=.46$, npv = .997, ppv = .70).
It is also interesting that although the attentional weighting ($W$) terms for the title and body were calibrated by the regression, they did not stray far from cognitively-plausible defaults
(see coefficients for title and body in Table \ref{tab:coeffs}).

>>>>

The final best-fit coefficients for each model component and formal statistical measurements are included in Tables \ref{tab:coeffs} and \ref{tab:fits} respectively.
Note that all four coefficients for the run are strong predictors of tag use ($p<.01$), and model fit is satisfactory (McFadden's pseudo $R_{}^{2}=.52$, npv = .994, ppv = .70).
It is also interesting that although the attentional weighting ($W$) terms for the title and body were calibrated by the regression, they did not stray far from cognitively-plausible defaults
(see coefficients for title and body in Table \ref{tab:coeffs}).
